### 2014-10-29 excersice 2/main.tex
asd

\section*{Q10}
\large{\textbf{
Name one     advantage and one disadvantage of having SIMD ISA extension instructions and FP instructions share resources. Explain your answers. Which specific resources are shared in the Intel     Pentium/MMX architecture? In the Sun Rock/Vis architecture? 5 points\\}}

%See RockIEEEmicro and marr_hyperthreading.

@@

\section*{Q20}
What network topology was used in the Connection Machine CM-5? Why? 5 points

@@

\section*{Q22}
\large{\textbf{
In what types of application areas are VLIW processors employed today? 2 points\\}}
In processing of digital signals (DSPs) and multimedia.

>>>>

\section*{Q10}
\large{\textbf{
Name one advantage and one disadvantage of having SIMD ISA extension instructions and FP instructions share resources. Explain your answers. Which specific resources are shared in the Intel Pentium/MMX architecture? In the Sun Rock/Vis architecture? 5 points\\}}
One advantage is that there is no need for adding additional hardware for keeping the architectural state and thus simplifies the design, while as the drawback is that you can not us FP instructions in the same routine as the added instructions and corruption of the data can occur. For the MMX architecture, the added registers maps onto the FP registers meaning these are shared between the two. 
%See RockIEEEmicro and marr_hyperthreading.

@@

\section*{Q20}
\large{\textbf{What network topology was used in the Connection Machine CM-5? Why? 5 points\\}}

@@

\section*{Q22}
\large{\textbf{In what types of application areas are VLIW processors employed today? 2 points\\}}
In processing of digital signals (DSPs) and multimedia.
